\LARGE \bf Children Teach a Robot to Write: A Teachable Robotic Agent which Engages in Simulated Handwriting

### 2014-12-11 main.tex
Forgot a bit of anonymity...
copyedit

\title{\LARGE \bf
% what about:
When Children Teach a Robot to Write
% ?
}

@@

The \emph{learning by teaching} paradigm, which engages the target student in
the act of teaching another, has been shown to produce motivational,
meta-cognitive, and educational benefits in a range of disciplines
\cite{Rohrbeck2003}. To our best knowledge, the application of the paradigm to
handwriting intervention remains however unexplored. One reason for this may due
to the requirement of an appropriately unskilled peer for the target child to
tutor, as this may present a logistical constraint if the target child is the
lowest performer in their class.  In some cases, it may be appropriate for a
peer or teacher to simulate a na\"ive learner for the target child to teach.
For handwriting, where one's skill level is visually evident, however, this
acting is likely to be eventually detected. As such, there is motivation for the
use of a teachable agent which can be configured for a variety of skill levels,
and for which children do not have preconceptions about its handwriting ability.

@@

Werfel suggests in~\cite{Werfel2014} that, until now, most of the work investigating how
humans can teach robots (in particular, physical skills) focuses on the robot's
benefits, and not so much on the learning experienced by the human tutor. Our
work focuses on this later aspect. A robotic learning agent which employs the learning by teaching paradigm has 
previously been developed by Tanaka and Matsuzoe~\cite{Tanaka2012}. In their
system, children learn vocabulary by teaching the {\sc nao} robot to act out 
verbs. The robot is tele-operated and mimics the actions that the children
teach it, but with no long-term memory or learning algorithm in place.

Our work significantly extends this line of work in two direction, first by
proposing an autonomous robotic partner, second by investigating the scaffolding
of children' acquisition of a challenging physical skill (handwriting).

@@

For the development of a learning algorithm in the context of
handwriting, a parameterisation of letters and their deformities has been sought such 
that different quality shapes can be generated, depending on the parameters input to
the letter models. This allows to configure the system such as to improve its writing 
by modifying the parameters based on feedback from the 
reinforcement learning partner (Section~\ref{sec:learningAlg}).

@@

Interestingly, although the parameters are the result of an \emph{unsupervised} 
shape analysis, they still represent variations which could have
been intuitively identified by a manual parameterisation. For example, for the
model shown in Figure \ref{fig:deviations_sPrint}, the parameters may represent
the height of the top half of the letter compared to the bottom half, the width
of the overall shape, etc. The ability to generate varied levels of deformations
which may be ascribed descriptive interpretations (not just numerical) is an
advantage of this method, given its intended use with humans: It is for instance
possible for a teacher to create initial letters with a particular feature (a wide
`s' or a `d' with a large loop, for example).

@@

In~\cite{Chandra2013}, Chandra found that children aged 4-6 years participating
in a handwriting peer tutoring pilot study most often made mistakes
qualitatively classified as inappropriate \emph{internal proportions} or
\emph{global deformations}. As exemplified in Figure \ref{fig:sampleLetters},
the shapes generated by the system exhibit the same kind of deformities. Chandra
identifies other, less common, mistakes that involve topological changes (like
letters being broken in subparts, extra strokes, etc.). Using a database of
children's letters when available may yield potential for better parameterizing
these other mistakes. However, as an initial approximation, the shape models
generated from PCA on a dataset of only adults' writing have shown to be
well-suited to generate `poor' letters that children were able to recognize and
successfully improve.

@@

In addition to constituting a technically novel system, the presented teachable
robotic agent represents a tool which may be used for investigating social and
pedagogical research questions. For example, one such question is what impact the addition of
such a teachable robotic agent would have on the outcomes of a typical
handwriting intervention. 
Preliminary studies at two schools in the Geneva area, involving above 50 children, 
have been conducted to evaluate the feasibility and technical soundness of the 
interaction system proposed as a tool for such investigations.

@@

How the children's perception of the robot as a learning agent may change over the 
long-term remains to be seen. On one occasion during the preliminary studies, a 
child's response to whether or not the {\sc nao} could write its own name included that it 
may have problems with the `n', as the child had been correcting the robot on this 
letter. This suggests that users may project human-like learning features, such as 
forgetfulness, onto the robot, which can be implemented 
in the learning agent. This may need to be capitalised on when considering how to 
extend the interaction for long time frames, as the present system -- with a learning rate 
such that progress is evident to the user -- will cause convergence for a letter within a 
few iterations.

@@

And the strong social impact of early educational problems makes continued research in this field
an undoubtedly meaningful challenge for robotics and human-robot interaction.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Anonymized for double-blind review
\section*{Acknowledgments}

This research was supported by the Swiss National Science Foundation through the
National Centre of Competence in Research Robotics.

>>>>

\title{\LARGE \bf
Children Teach a Robot to Write: A Teachable Robotic Agent which Engages in Simulated Handwriting %still not sure
% what about:
% When Children Teach a Robot to Write
% ?
}

@@

The \emph{learning by teaching} paradigm, which engages the target student in
the act of teaching another, has been shown to produce motivational,
meta-cognitive, and educational benefits in a range of disciplines
\cite{Rohrbeck2003}. To our best knowledge, the application of the paradigm to
handwriting intervention remains, however, unexplored. One reason for this may due
to the requirement of an appropriately unskilled peer for the target child to
tutor, as this may present a logistical constraint if the target child is the
lowest performer in their class.  In some cases, it may be appropriate for a
peer or teacher to simulate a na\"ive learner for the target child to teach.
For handwriting, where one's skill level is visually evident, however, this
acting is likely to be eventually detected. As such, there is motivation for the
use of a teachable agent which can be configured for a variety of skill levels,
and for which children do not have preconceptions about its handwriting ability.

@@

Werfel suggests in~\cite{Werfel2014} that, until now, most of the work investigating how
humans can teach robots (in particular, physical skills) focuses on the robot's
benefits, and not so much on the learning experienced by the human tutor. Our
work focuses on this latter aspect. A robotic learning agent which employs the learning by teaching paradigm has 
previously been developed by Tanaka and Matsuzoe~\cite{Tanaka2012}. In their
system, children learn vocabulary by teaching the {\sc nao} robot to act out 
verbs. The robot is tele-operated and mimics the actions that the children
teach it, but with no long-term memory or learning algorithm in place.

Our work significantly extends this line of work in two directions, first by
proposing an autonomous robotic partner, second by investigating the context
of children's acquisition of a challenging physical skill (handwriting).

@@

For the development of a learning algorithm in the context of
handwriting, a parameterisation of letters and their deformities has been sought such 
that different quality shapes can be generated, depending on the parameters input to
the letter models. This allows us to configure the system such as to improve its writing 
by modifying the parameters based on feedback from the 
reinforcement learning partner (Section~\ref{sec:learningAlg}).

@@

Interestingly, although the parameters are the result of an \emph{unsupervised} 
shape analysis, they still represent variations which could have
been intuitively identified by a manual parameterisation. For example, for the
model shown in Figure \ref{fig:deviations_sPrint}, the parameters may represent
the height of the top half of the letter compared to the bottom half, the width
of the overall shape, etc. The ability to generate varied levels of deformations
which may be ascribed descriptive interpretations (not just numerical) is an
advantage of this method, given its intended use with humans. It is, for instance,
possible for a teacher to create initial letters with a particular feature (a wide
`s' or a `d' with a large loop, for example).

@@

In~\cite{Chandra2013}, Chandra found that children aged 4-6 years participating
in a handwriting peer tutoring pilot study most often made mistakes
qualitatively classified as inappropriate \emph{internal proportions} or
\emph{global deformations}. As exemplified in Figure \ref{fig:sampleLetters},
the shapes generated by the system exhibit the same kind of deformities. Chandra
identifies other, less common, mistakes that involve topological changes (like
letters being broken in subparts, extra strokes, etc.). Using a database of
children's letters when available may yield potential for better parameterising
these other mistakes. However, as an initial approximation, the shape models
generated from PCA on a dataset of only adults' writing have shown to be
well-suited to generate `poor' letters that children were able to recognise and
successfully improve.

@@

In addition to constituting a technically novel system, the presented teachable
robotic agent represents a tool which may be used for investigating social and
pedagogical research questions. For example, one such question is what impact the addition of
such a teachable robotic agent would have on the outcomes of a typical
handwriting intervention. 
Preliminary studies at two schools in the Geneva area, involving over 50 children, 
have been conducted to evaluate the feasibility and technical soundness of the 
interaction system proposed as a tool for such investigations.

@@

How the children's perception of the robot as a learning agent may change over the 
long-term remains to be seen. On one occasion during the preliminary studies, a 
child's response to whether or not the {\sc nao} could write its own name included that it 
may have problems with the `n', as the child had been correcting the robot on this 
letter. This suggests that users may project human-like learning features, such as 
forgetfulness, onto the robot, whether or not they are technically present.
This may need to be capitalised on when considering how to 
extend the interaction for long time frames, as the present system -- with a learning rate 
such that progress is evident to the user -- will cause convergence for a letter within a 
few iterations.

@@

The strong social impact of early educational problems makes continued research in this field
an undoubtedly meaningful challenge for robotics and human-robot interaction.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Anonymized for double-blind review
%\section*{Acknowledgments}
%
%This research was supported by the Swiss National Science Foundation through the
%National Centre of Competence in Research Robotics.
